2-factor-Hull-White\_model\_calibration

### 2020-05-10 week7/Report.tex
Added Report + Intro

\title{Price a Vanilla European Call Option}

@@

\date{April. 26, 2020} % if this is omitted, the current date is used for the title page
\maketitle

\noindent
\textbf{Keywords:} European Options, Heston model,  Constant Elasticity of Variance (CEV) model and Stochastic Volatility.

% the following creates an abstract -- it can be omitted
% an example of an environment: these have the form \begin{name} ... \end{name}
\begin{abstract}
    In this paper, we price a vanilla European call option under the Heston model and then simulate the monthly share price over a year using the Constant Elasticity of Variance (CEV) model, with the assumption of constant volatility each month. Monte Carlo simulations with varying sample sizes are run and the results are plotted against the closed form value for comparison.
\end{abstract}

@@

In this paper we go beyond the constant volatility assumption in the Black-Scholes model.  Most of code implemented in this submission is derived from Module 5 \cite{M5} of the course.

@@

\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The current share price is \$100
    \item The risk-free continuously compounded interest rate is 8\%
    \item The volatility for the underlying share is 30\%
\end{itemize}

\section{Fourier pricing technique under Heston model dynamics
}

Black-Scholes option pricing models assumed volatility of the underlying assets to be constant or a predetermined function of time, we will now implement a model which features instantaneous variance of asset price using volatility that evolves stochastically in time. Although there are several models incorporating stochastic volatility including introduced by Hull and White \cite{HW1}, Stein and Stein \cite{SS1} and Heston \cite{Heston1} \cite{Heston2}, we will implement Heston's constant interest rate model.

With the assumption that the underlying share follows the Heston model dynamics, the additional parameters required are specified as follows:
\begin{itemize}
    \item $\nu_0 = 0.06$
    \item $\kappa = 9$
    \item $\theta = 0.06$
    \item $\rho = -0.4$
\end{itemize}

    The Characteristic function is implemented using a function presented by
Albrecher et al \cite{AMST1}. The function is written as:
\[\phi_{S_T} = exp(C(\tau;u)+D(\tau;u)v_t + iu \log(S_t) )\]

Where,

\[C(\tau;u) = ri\tau u + \theta \kappa [\tau x\_ - \frac{1}{a}\log(\frac{1-ge^{d\tau}}{1-g})],\]

\[D(\tau;u) = (\frac{1-e^{d\tau}}{1-ge^{d\tau}})x\_,\]

\[\tau = T -t ,\]

\[ g = \frac{x\_}{x_+},\]

\[ x_\pm = \frac{b\pm d}{2a},\]

\[ d = \sqrt{b^2 - 4ac},\]

\[ c = - \frac{u^2 + ui}{2},\]

\[ b = \kappa - \rho \sigma iu,\]

\[ a = \frac {\sigma^2}{2}\]

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Characteristic function code}

\PY{n}{a} \PY{o}{=} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}

\PY{k}{def} \PY{n+nf}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{kappa} \PY{o}{\PYZhy{}} \PY{n}{rho}\PY{o}{*}\PY{n}{sigma}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}

\PY{k}{def} \PY{n+nf}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{u}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{+}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}

\PY{k}{def} \PY{n+nf}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{\PYZhy{}}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{a}\PY{o}{*}\PY{n}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{+}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{n}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{n}{val1} \PY{o}{=} \PY{n}{T}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{a}
    \PY{k}{return} \PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u} \PY{o}{+} \PY{n}{theta}\PY{o}{*}\PY{n}{kappa}\PY{o}{*}\PY{n}{val1}

\PY{k}{def} \PY{n+nf}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{n}{val1} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
    \PY{n}{val2} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
    \PY{k}{return} \PY{p}{(}\PY{n}{val1}\PY{o}{/}\PY{n}{val2}\PY{p}{)}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)} \PY{o}{+} \PY{n}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{v0} \PY{o}{+} \PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{adj\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}\PY{o}{/}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    Now we vectorize the code, calculate an estimate for integrals and
calculate the Fourier estimate of our call price.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{delta\PYZus{}t} \PY{o}{=} \PY{n}{t\PYZus{}max}\PY{o}{/}\PY{n}{N}
\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,}\PY{n}{N}\PY{p}{,}\PY{n}{N}\PY{p}{)}
\PY{n}{t\PYZus{}n} \PY{o}{=} \PY{p}{(}\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}

\PY{c+c1}{\PYZsh{}Integral calculations}
\PY{n}{first\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{adj\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
\PY{n}{second\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}

\PY{c+c1}{\PYZsh{}Call value}
\PY{n}{fourier\PYZus{}call\PYZus{}val} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{first\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{second\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}
\PY{n}{fourier\PYZus{}call\PYZus{}val}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
13.734895692109077
\end{Verbatim}
\end{tcolorbox}

    To see the effectiveness of the pricing option under Heston dynamics we
will also price the call option under Black-Scholes assumption.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} Code for analytical solution for vanilla European Call option}
\PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{o}{/}\PY{n}{K}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{r} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}
\PY{n}{d\PYZus{}2\PYZus{}stock} \PY{o}{=} \PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}

\PY{n}{analytic\PYZus{}callprice} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}1\PYZus{}stock}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}2\PYZus{}stock}\PY{p}{)}
\PY{n}{analytic\PYZus{}callprice}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
15.711312547892973
\end{Verbatim}
\end{tcolorbox}

\section{Simulate a share price path using CEV Model
}
Cox \cite{Cox1} developed the constant elasticity of variance (CEV) option pricing model, it attempts to capture stochastic volatility and is given by:

\[dS_t =  \mu S_t dt + \sigma  S^\gamma _t dW_t\]

If $\gamma = 1$ this model return the same value as Black-Scholes model, however if the value of $\gamma < 1 $ we experience an effect called leverage effect where the volatility increases as the price decreases over subsequent time periods.

Based on the assumption that $\sigma(t_i,t_{i+1}) = \sigma(S_{ti})^{\gamma-1}$, where $\sigma = 0.3$ and $\gamma = 0.75$.  We can simulate the next step in a share price path using the following formula:
$$S_{t_{i+1}} = S_{t_i}e^{(r - \frac{\sigma^2 (t_i,t_{i+1})}{2})(t_{i+1}-t_i)+\sigma(t_i, t_{i+1})\sqrt{t_{i+1}-t_i}Z}$$
where $S_{ti}$ is the share price at time $t_i$, $\sigma(t_i, t_{i+1})$ is the volatility for the period $[t_i,t_{i+1}]$, r is the risk-free interest rate, and Z~N(0, 1)

First, we define our helper functions. The next\_share\_price function
is used to calculate the evolution of the share price at t+1, from the
share price at t. We generate the random variable Z from within this
function. The effective sigma is also written as a function of the share
price at t.

Just for exploration purposes, we also added a varying\_vol flag, to
allow us to switch between a constant volatility and varying volatility.
We use the initial stock price instead of the previous price when
assuming a contant volatility.

The other function is the generate\_share\_price\_path function. We
first create an empty numpy array of shape (sample\_size x timesteps+1).
Note the addition of one element to the timestep, as the first element
is equal to the initial stock price. We then iterate through each path,
and each timestep, applying the next\_share\_price function against the
previous share price. We then convert the result into a pandas DataFrame
and return the results.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{7}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{dT}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
    \PY{n}{Z} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size}\PY{o}{=}\PY{n}{sample\PYZus{}size}\PY{p}{)}
    \PY{k}{if} \PY{n}{varying\PYZus{}vol}\PY{p}{:}
        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
    \PY{k}{else}\PY{p}{:}
        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}

    \PY{k}{return} \PY{n}{prev\PYZus{}price}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{r}\PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{sigma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
    \PY{n}{df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{p}{[}\PY{n}{S0}\PY{p}{]}\PY{o}{*}\PY{n}{sample\PYZus{}size}\PY{p}{)}
    \PY{k}{for} \PY{n}{t} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{timesteps}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{:}
        \PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{p}{]} \PY{o}{=} \PY{n}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{p}{)}
    \PY{k}{return} \PY{n}{df}\PY{o}{.}\PY{n}{T}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{8}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{patches} \PY{k}{as} \PY{n+nn}{mpatches}
\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{10}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}

\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{)}
\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{l+m+mf}{1.0}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Timestep}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{red\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CEV}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{blue\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{BSM}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{handles}\PY{o}{=}\PY{p}{[}\PY{n}{red\PYZus{}patch}\PY{p}{,} \PY{n}{blue\PYZus{}patch}\PY{p}{]}\PY{p}{,} \PY{n}{loc}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{upper left}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CEV vs BSM Stock Price Paths}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Next, we create a python dictionary called share\_price\_paths, to hold
our results for part 2. The key of this dictionary would be the number
of sample price paths, while the values would be the dataframes
containing the price paths. We also track the rough processing time
required at each step, by printing the time when each iteration
completes.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{9}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{time}

\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}

\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

>>>>

\title{Simulate Asset Price Evolutions and Reprice Risky up-and-out Call Option}

@@

\date{May. 10, 2020} % if this is omitted, the current date is used for the title page
\maketitle

\noindent
\textbf{Keywords:} European Options, Non-constant interest rate,  Local volatility, LIBOR forward rates, Zero-coupon bond and Stochastic Volatility.

% the following creates an abstract -- it can be omitted
% an example of an environment: these have the form \begin{name} ... \end{name}
\begin{abstract}
This report presents the results of the simulation of a European up-and-out call option over twelve months, but the difference between this submission and submission 1 is the implementation of a non-constant interest rate and local volatility.  We use LIBOR forward rate model to simulate interest rates.  We also use discount factor to value the option without default risk and then the value of the option with counterparty default risk.

\end{abstract}

@@

In this paper we go beyond the constant risk-free continuously compounded rate.  There are several models to implement stochastic interest rates.  The short rate models which describe instantaneous continuously-compounded interest rate at time $t , r_t$ include the Vasicek model introduced in \cite{Vas1}, Mamon in \cite{Mamon1} advances this model by presenting approaches in obtaining the closed-form solution using the Vasicek model. Under the Vasicek model the short rate dynamics is given by,\\

\[
d r_t= \alpha (b - r_t) dt + \sigma dW_t
\]

Where $W_t$ is Brownian motion, $b$ is the level to which the short rate will tend in the long run, $\alpha$ is the rate at which the short rate will tend towards $b$ and $\sigma$ is the volatility of the short rate.  The stochastic differential equation can be solved to give $r_t$

\[
r_t= e^{-\alpha t} [r_0 + b(e^{\alpha t} - 1)+\int^t_0 \sigma e^{\alpha s} dW_s ] 
\]
\\

Cox, Ingersoll and Ross also presented a stochastic differential equation for short term rates in \cite{CIR1} given by
\[
d r_t= \alpha (b - r_t) dt + \sigma \sqrt{r_t} dW_t
\]
This model prevents the short from becoming 0 but offers no closed form solution\\

The Hull-White model described in \cite{HW1} also presents stochastic differential equation for the short term rate,

\[
d r_t= (\theta(t) - \alpha(t) r_t) dt + \sigma (t) dW_t
\]
where $\theta(t) = \alpha b$ which is a non constant term, allowing the mean reversion level to vary. \\

The model we implement in this assignment is the LIBOR forward rate model to simulate interest rates.  The initial values for the LIBOR forward rates need to be calibrated to the market forward rates which can be deduced through the market zero-coupon bond prices. This continuously compounded interest rate is given by,

\[
e^{r_{ti} (t_{i+1} - t_i)}= 1 + L(t_i,t_{i+1})(t_{i+1} -t_i )
\]

Most of code implemented in this submission is derived from Module 6 \cite{M6} and Module 7 \cite{M7} of the course.

@@

\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The current share price is \$100
    \item The up-and-out barrier for the option is \$150
    \item The risk-free continuously compounded interest rate is 8\%
    \item The volatility for the underlying share is 30\%
    \item The volatility for counterparty's firm value is 25\%
    \item The counterparty's debt, due in one year, is  \$175
    \item The current firm value for the counterparty is \$200
    \item The correlation between the counterparty and the stock is constant at 0.2
    \item The recovery rate with the counterparty is 25\%

\end{itemize}

\section{LIBOR forward rates, stock paths, and counterparty firm values.
}

\section{Discount factor and Value of the Option
}
